---
title: "Assignment 8 Question 2"
author: "Tan, Zhenhao; Thomas, William; Yan, Chengdong"
output: html_document
---

First we load the required packages
```{r}
library("lmtest")
library("car")

```

Below we define  *HEDGP* that generates data in accordance to the heteroskedastic data generating process as described in the question, and *HODGP*, which generates homoskedastic data as required in part c and d. 
```{r}
HEDGP = function(n){
	X = c(rnorm(n,0,1))
	U = X * c(runif(n,-1,1))
	Y = c(rep(1,n)) + X + U 
	return(rbind(Y,X,U))
}

HODGP = function(n){
	X = c(rnorm(n,0,1))
	U = c(runif(n,-1,1))
	Y = c(rep(1,n)) + X + U 
	return(rbind(Y,X,U))
}



```


We also define the Montecarlo function which would output the required statistics, depending on the data generating process.

```{r}

MC = function(DG, n){
	hconfint = c(rep(0,1000))
	h0confint = c(rep(0,1000))
	h2confint = c(rep(0,1000))
	h3confint = c(rep(0,1000))

	hconfintcount = 0
	h0confintcount = 0
	h2confintcount = 0
	h3confintcount = 0

    for (i in (1:1000)) {
    	D = DG(n)
    	Y = D[1,]
    	X = D[2,]
        reg1 = lm(Y ~ X)
        #homoskedastic confint, check if true parameter is in homoskedastic confint
        if (confint(reg1)[2,][2] > 1 & confint(reg1)[2,][1] < 1) {hconfintcount = hconfintcount + 1}
        hconfint[i] = confint(reg1)[2,][2] - confint(reg1)[2,][1]

        #H0 confint, same principle applies
        H0 = coeftest(reg1, vcov=hccm(reg1,type="hc0"))
        if (confint(H0)[2,][2] > 1 & confint(H0)[2,][1] < 1) {h0confintcount = h0confintcount + 1}
        h0confint[i] = confint(H0)[2,][2] - confint(H0)[2,][1]
        
        #H2 confint
        H2 = coeftest(reg1, vcov=hccm(reg1,type="hc2"))
        if (confint(H2)[2,][2] > 1 & confint(H2)[2,][1] < 1) {h2confintcount = h2confintcount + 1}
        h2confint = confint(H2)[2,][2] - confint(H2)[2,][1]
        
        #H3 confint, check coverage, add 
        H3 = coeftest(reg1,vcov=hccm(reg1,type="hc3"))
        if (confint(H3)[2,][2] > 1 & confint(H3)[2,][1] < 1) {h3confintcount = h3confintcount + 1}
        h3confint = confint(H3)[2,][2] - confint(H3)[2,][1]

	}


	return(rbind(hconfintcount/1000, mean(hconfint), h0confintcount/1000, mean(h0confint), h2confintcount/1000, mean(h2confint), h3confintcount/1000, mean(h3confint)))

}


```


```{r}
D1 = MC(HEDGP, 30)
paste0("Coverage of Homoskedastic confint is ", D1[1])
paste0("Average length of  Homoskedastic confint is ", D1[2])
paste0("Coverage of H0 confint is ", D1[3])
paste0("Average length of  H0 confint is ", D1[4])
paste0("Coverage of H2 confint is ", D1[5])
paste0("Average length of  H2 confint is ", D1[6])
paste0("Coverage of H3 confint is ", D1[7])
paste0("Average length of  H3 confint is ", D1[8])
```

H3 has the greatest coverage, but homoskedastic confint is the smallest 

```{r}
D2 = MC(HEDGP, 1000)
paste0("Coverage of Homoskedastic confint is ", D2[1])
paste0("Average length of  Homoskedastic confint is ", D2[2])
paste0("Coverage of H0 confint is ", D2[3])
paste0("Average length of  H0 confint is ", D2[4])
paste0("Coverage of H2 confint is ", D2[5])
paste0("Average length of  H2 confint is ", D2[6])
paste0("Coverage of H3 confint is ", D2[7])
paste0("Average length of  H3 confint is ", D2[8])
```

H3 has the greatest coverage, which exceeds 0.95. But homoskedastic confint is the smallest
```{r}
D3 = MC(HODGP, 30)
paste0("Coverage of Homoskedastic confint is ", D3[1])
paste0("Average length of  Homoskedastic confint is ", D3[2])
paste0("Coverage of H0 confint is ", D3[3])
paste0("Average length of  H0 confint is ", D3[4])
paste0("Coverage of H2 confint is ", D3[5])
paste0("Average length of  H2 confint is ", D3[6])
paste0("Coverage of H3 confint is ", D3[7])
paste0("Average length of  H3 confint is ", D3[8])
```

The homoskedastic confint has the greatest coverage, and H2 confint is the smallest in length 

```{r}
D4 = MC(HODGP, 1000)
paste0("Coverage of Homoskedastic confint is ", D4[1])
paste0("Average length of  Homoskedastic confint is ", D4[2])
paste0("Coverage of H0 confint is ", D4[3])
paste0("Average length of  H0 confint is ", D4[4])
paste0("Coverage of H2 confint is ", D4[5])
paste0("Average length of  H2 confint is ", D4[6])
paste0("Coverage of H3 confint is ", D4[7])
paste0("Average length of  H3 confint is ", D4[8])
```

There are no significant differences between coverage of the different confidence intervals, nor are there significant differences between the confidence intervals in this case where n = 1000

However, across the different example size, HC3 confidence interval gives the most reliable performance: it consistently gives a coverage near 0.95 in both small (n = 30) and large (n = 1000) samples



